Matched Source Waveform Inversion for Transmitted Waves

### 2024-06-02 repro/papers/awinum/paper.tex
added cam

\subsection{Non-smooth models: the Camembert}

>>>>

\subsection{Recovering a Camembert: effect of non-smoothness}

\plot{cambulk}{width=\textwidth}{A model resembling the ``camembert''
  of \cite{GauTarVir:86}. Diameter of circular inclusion = 2500 m,
  approximately 8 wavelengths at median frequency. Interior value 20\%
above exterior (4.8 GPa vs 4.0 GPa).}

\plot{camcwd20}{width=\textwidth}{Data generated using ``camembert''
  model (Figure \ref{fig:cambulk}), same source-receiver geometry as
  in Figure \ref{fig:dcwd20}: 20 sources located at $x=2000$ m, spaced
  150 m apart, starting at $z=500$ m; 201 receivers located at $x=6000$ m,
  spaced 20 m apart, starting at $z=200$ m.}

\plot{cam20uest0}{width=\textwidth}{Adaptive filter required to produce the data
of Figure \ref{fig:camcwd20} from corresponding homogeneous medium data (Figure
\ref{fig:chwd20}).}

\plot{cam20mestmswi}{width=\textwidth}{Result of 12 MSWI
  iterations applied to the data in Figure \ref{fig:camcwd20}, beginning
  at the homogeneous model.}

\multiplot{2}{cam20resimmestmswi,cam20residmestmswi}{width=0.45\textwidth}
{a: Data  corresponding to MSWI result shown in Figure
  \ref{fig:cam20mestmswi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:cam20resimmestmswi} and target data
  \ref{fig:camcwd20}.}

\plot{cam20uestmswi}{width=\textwidth}{Adaptive filter estimate for MSWI
  inversion shown in Figure \ref{fig:cam20mestmswi}.}

\plot{cam20mestmswifwi}{width=\textwidth}{Bulk modulus produced by 12
  steepest descent steps to minimize the FWI objective \ref{eqn:fwi},
  using the data shown in \ref{fig:camcwd20}, and starting at the MSWI
  result shown in Figure \ref{fig:cam20mestmswi}.}

\multiplot{2}{cam20resimmestmswifwi,cam20residmestmswifwi}{width=0.45\textwidth}{a: Data
  corresponding to FWI + MSWI result shown in Figure
  \ref{fig:cam20mestmswifwi}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:cam20resimmestmswifwi} and target data
  \ref{fig:camcwd20}.}

\plot{cam20uest1}{width=\textwidth}{Adaptive filter to match
  data for FWI + MSWI model (Figure \ref{fig:cam20resimmestmswi}) to ``camembert'' 
  data (Figure \ref{fig:camcwd20}).}

\plot{cam20mestmswifwifine}{width=\textwidth}{``Hi-res'' bulk modulus produced by
  25 additional steepest descent steps, with inverse weight operator =
  2 point moving average in both directions, repeated once, and
  initial bulk modulus = output of first FWI + MSWI cycle (Figure
  \ref{fig:cam20mestmswifwi}). Note that top and bottom edges of disk
  shown in Figure \ref{fig:cambulk} are clearly visible.}

\multiplot{2}{cam20resimmestmswifwifine,cam20residmestmswifwifine}{width=0.45\textwidth}{a: Data
  corresponding to hi-res FWI + MSWI result shown in Figure
  \ref{fig:cam20mestmswifwifine}. b: Residual or data error - difference between
  data shown in Figure \ref{fig:cam20resimmestmswifwifine} and target data
  \ref{fig:camcwd20}.}

\plot{cam20uest2}{width=\textwidth}{Adaptive filter to match
  data for hi-res FWI + MSWI model (Figure \ref{fig:cam20resimmestmswi}) to ``camembert'' 
  data (Figure \ref{fig:camcwd20}).}
